SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-06 scipy-1.0/paper.tex
Expand description of scikits

By the middle to late 2000s, SciPy was starting to mature after a long phase of significant
growth and adoption. The scope of the SciPy library
narrowed, while the breadth of the ecosystem grew
through a new type of auxiliary package: the scikit\cite{scikits-general}.
The tooling, development, documentation, and release processes became more professional.
SciPy was expanded carefully, with the patience affordable in open source
projects and via best practices common in industry \cite{millman2014developing}.

>>>>

By the middle to late 2000s, SciPy was starting to mature after a long phase of significant
growth and adoption. The scope of the SciPy library
narrowed, while the breadth of the ecosystem grew
through a new type of auxiliary package: the
scikit\cite{scikits-general}, a complementary library
developed outside of SciPy, allowing for more rapid exploration of
experimental ideas while maintaining familiar style and development methodology.
In SciPy itself, tooling, development, documentation, and release processes became more professional.
The library was expanded carefully, with the patience affordable in open source
projects and via best practices common in industry \cite{millman2014developing}.
